InnoDB Full text Search hacking with Shiny/R

### 2015-12-28 article.rmd
-
Changed the string connection.

# You do not want clear passwords, but is a sandbox.
con <- dbConnect(MySQL(), 
                 user="msandbox", password="msandbox", port=14901 
                 ,dbname="test", socket="/tmp/mysql_sandbox14901.sock", 
                 host="127.0.0.1")

@@

@@

- Use QUERY EXPANSION only if you are interested to search relations over exact matches. Remember that the field
  size is crucial when using this.
- FTS is not the best fit for exact string matches. You won't use FTS for searching emails or strings as words using
  single fields. 
- If you are using BOOLEAN MODE, you can use the rank score to filter rows. MySQL is clever enough to optimize the 
  FTS functions to avoid double executions. You can do this using somehting like:
  `match(content,title) against ("first (<second >third)") > 1 `
  Generally, scores lower than 1 can be ignored when using boolean or natural mode searches. 
- `OPTIMIZE TABLE` does a rebuild of the table. To avoid this, set `innodb_optimize_fulltext_only=1` in order to do an incremental
  maintance on the table.
- Recall that NATURAL LANGUAGE MODE does not take the operands as the BOOLEAN MODE.
- If you plan to order by rank, it is not necessary to specify the clause `ORDER BY` as MySQL does the order forcelly internally. Also,
  the behavior is different from the default as it returns the heaviest at the top (like ORDER BY rank DESC).
- If you come from MyISAM's FTS implementation, recall that the ranking scoring is different.
- Try to don't use more than one FTS expression in the where clause. Keep in mind that this affects the order in the results and
  it consumes a considerably amount of CPU. MySQL orders by the latest expression in the WHERE clause. [WL#7123](https://dev.mysql.com/worklog/task/?id=7123)
- Also, if avoiding the rank information in the projection (SELECT clause) and using other aggregations like count(*), will use
  the "no ranking" FT_hints. The `limit` hint won't be used if invoked explicitely an `ORDER BY` and th `MATCH` clause in the projection.

>>>>

# You do not want clear passwords, but is a sandbox.
#con <- dbConnect(MySQL(), 
#                 user="msandbox", password="msandbox", port=14901 
#                 ,dbname="test", socket="/tmp/mysql_sandbox14901.sock", 
#                 host="127.0.0.1")

con <- dbConnect(MySQL(), 
                 user="ftsinnodb", password="elfilete", port=3306 
                 ,dbname="ftsinnodb", #socket="/tmp/mysql_sandbox14901.sock", 
                 host="db4free.net")

@@

Thanks db4free.net for the MySQL free online database!

@@

- Use QUERY EXPANSION only if you are interested to search relations over exact matches. Remember that the field
  size is crucial when using this.
- FTS is not the best fit for exact string matches. You won't use FTS for searching emails or strings as words using
  single fields. 
- If you are using BOOLEAN MODE, you can use the rank score to filter rows. MySQL is clever enough to optimize the 
  FTS functions to avoid double executions. You can do this using somehting like:
  `match(content,title) against ("first (<second >third)") > 1 `
  Generally, scores lower than 1 can be ignored when using boolean or natural mode searches. 
- `OPTIMIZE TABLE` does a rebuild of the table. To avoid this, set `innodb_optimize_fulltext_only=1` in order to do an incremental
  maintance on the table.
- Recall that NATURAL LANGUAGE MODE does not take the operands as the BOOLEAN MODE.
- If you plan to order by rank, it is not necessary to specify the clause `ORDER BY` as MySQL does the order forcelly internally. Also,
  the behavior is different from the default as it returns the heaviest at the top (like ORDER BY rank DESC).
- If you come from MyISAM's FTS implementation, recall that the ranking scoring is different.
- Create the FULLTEXT index after the data is loaded [InnoDB bulk load](http://dev.mysql.com/doc/refman/5.7/en/optimizing-innodb-bulk-data-loading.html). When restoring FTS backups, you will probably hit the "ERROR 182 (HY000) at line nn: Invalid InnoDB FTS Doc ID".
- Try to don't use more than one FTS expression in the where clause. Keep in mind that this affects the order in the results and
  it consumes a considerably amount of CPU. MySQL orders by the latest expression in the WHERE clause. [WL#7123](https://dev.mysql.com/worklog/task/?id=7123)
- Also, if avoiding the rank information in the projection (SELECT clause) and using other aggregations like count(*), will use
  the "no ranking" FT_hints. The `limit` hint won't be used if invoked explicitely an `ORDER BY` and th `MATCH` clause in the projection.
